\newpage
\section{Introduction}
In recent years, online travel booking systems have transformed the way people plan and book their trips. The increasing demand for seamless, user-friendly platforms has made it essential for travel agencies to offer online services that cater to diverse customer needs. This project proposes the development of a Travel Agency website, aimed at providing users with a convenient way to explore and select tour packages from various countries. The platform will allow users to log in, browse available travel options, select packages, and customize their experience by choosing flight and hotel types before proceeding to a secure payment gateway. Additionally, the administrative side of the system will allow administrators to manage packages, including adding or modifying tour guide details.

The motivation behind this project stems from the growing trend of online travel services and the need for travel agencies to maintain competitive, user-friendly platforms. By streamlining the booking process, this project aims to enhance user experience while simplifying administrative tasks. The significance of this project lies in its potential to modernize and simplify the travel booking process, making it more accessible to a wide range of customers. The proposed system's scope includes developing the user interface, integrating payment gateways, and creating an admin panel for managing packages and guide information, thus covering both user and admin perspectives to ensure a well-rounded solution.
