\section{Objectives}

\begin{enumerate}
    \item \textbf{Develop a User-Friendly Interface}  
    \begin{itemize}
        \item \textbf{Specific}: Create an intuitive and responsive website interface that allows users to browse and select tour packages, choose flight and hotel types, and proceed to a payment gateway.  
        \item \textbf{Measurable}: Ensure the website is fully functional on desktop and mobile devices with at least 90\% user satisfaction in usability tests.  
        \item \textbf{Achievable}: Leverage modern web development technologies such as Node.js, Next.js, and Tailwind CSS to build the interface.  
        \item \textbf{Relevant}: This objective addresses the need for a seamless and convenient user experience.  
        \item \textbf{Time-bound}: Complete within the first 2 months of the project timeline.
    \end{itemize}

    \item \textbf{Implement Secure Payment Gateway Integration}  
    \begin{itemize}
        \item \textbf{Specific}: Integrate a reliable and secure payment gateway to handle user transactions when booking tour packages.  
        \item \textbf{Measurable}: Successfully complete payment transactions in at least 95\% of test cases with no security vulnerabilities.  
        \item \textbf{Achievable}: Use trusted APIs and payment systems such as Stripe or PayPal for integration.  
        \item \textbf{Relevant}: This ensures that users can make secure payments, directly addressing the issue of manual payment handling.  
        \item \textbf{Time-bound}: Implement within 3 months of the project timeline.
    \end{itemize}

    \item \textbf{Develop Admin Panel for Package and Guide Management}  
    \begin{itemize}
        \item \textbf{Specific}: Build an admin interface that allows easy CRUD operations on tour packages and the addition of local tour guide information.  
        \item \textbf{Measurable}: Ensure the admin panel has full functionality for managing at least 50 tour packages and guide details.  
        \item \textbf{Achievable}: Use MySQL for database management and integrate with the website’s backend system.  
        \item \textbf{Relevant}: This directly addresses the inefficiencies in current systems for package and guide management.  
        \item \textbf{Time-bound}: Complete the admin panel within 4 months.
    \end{itemize}

    \item \textbf{Ensure System Scalability and Performance Optimization}  
    \begin{itemize}
        \item \textbf{Specific}: Optimize the website's backend for performance, ensuring that it can handle a large volume of concurrent users and data.  
        \item \textbf{Measurable}: Achieve load times under 2 seconds and handle up to 500 simultaneous users in stress tests.  
        \item \textbf{Achievable}: Utilize best practices for web performance and use efficient database queries and caching mechanisms.  
        \item \textbf{Relevant}: Ensuring scalability will allow the system to accommodate growth and handle peak traffic periods.  
        \item \textbf{Time-bound}: Complete optimization within the final month of the project.
    \end{itemize}

    \item \textbf{Conduct User Testing and Feedback Collection}  
    \begin{itemize}
        \item \textbf{Specific}: Perform user testing with at least 30 participants to gather feedback on usability, design, and functionality.  
        \item \textbf{Measurable}: Collect and analyze feedback with a goal of improving the system based on at least 80\% of the user suggestions.  
        \item \textbf{Achievable}: Organize user testing sessions through surveys and usability tests.  
        \item \textbf{Relevant}: This will ensure that the platform meets user expectations and functions as intended.  
        \item \textbf{Time-bound}: Conduct testing during the last 2 weeks of the project.
    \end{itemize}
\end{enumerate}

By achieving these objectives, the project will significantly improve the travel booking process, ensuring ease of use for customers and efficiency for administrators.
