\subsection{Introduction}
With the continuous advancement of internet technologies and digital solutions, the travel and tourism industry has experienced a significant transformation. Travelers now prefer online platforms that allow them to browse, compare, and book travel packages from the comfort of their homes. In response to this demand, we have developed a web-based application titled \textbf{Odyssey Travel Agency Software}, a full-stack solution that enables users to plan their international tours efficiently. 

This application allows users to register and log into the system, explore various tour packages offered across different countries, and make customized selections based on their preferences. Once a package is chosen, users can select specific flight and hotel types before proceeding to a secure online payment gateway. In addition to enhancing the user experience, the system also includes an admin panel that facilitates management operations such as adding, updating, or removing packages and assigning local tour guides. 

The frontend is implemented using HTML, CSS, Tailwind CSS, JavaScript, and Next.js, ensuring responsiveness and ease of use. On the backend, Laravel and MySQL provide a robust framework for secure data handling and server-side logic.

\subsection{Motivation}
The idea for developing this travel agency software was motivated by the inefficiencies and limitations observed in traditional travel booking systems. Often, travelers have to rely on physical offices, manual communications, and paper-based confirmations, which can be time-consuming, error-prone, and inconvenient, especially for international tours. Moreover, travel agencies struggle to update package offerings dynamically and manage client records efficiently.

Our motivation was to bridge this gap by offering a complete, user-friendly, and automated system that improves accessibility and streamlines both user and admin experiences. We wanted to create a platform where users could enjoy end-to-end tour planning with real-time access to tour packages, flexible booking options, and secure transactions. Simultaneously, we aimed to empower travel agencies with tools for managing tour information, local guides, and customer interactions, ultimately contributing to better service quality and operational productivity.

\subsection{Application}
The Odyssey Travel Agency Software includes two major interfaces—\textbf{User Panel} and \textbf{Admin Panel}—each serving a distinct purpose and audience:

\textbf{User Panel:}
\begin{itemize}
    \item Allows users to register, login, and access their dashboard securely.
    \item Users can view various international tour packages categorized by destination countries.
    \item Each package contains details such as price, duration, itinerary, included services, and available customization.
    \item After selecting a tour, users can choose the type of flight (e.g., economy, business class) and hotel (e.g., 3-star, 5-star) based on their budget and comfort.
    \item Users are then redirected to a payment gateway to complete the booking securely.
    \item The booking history is saved and accessible from the user’s profile.
\end{itemize}

\textbf{Admin Panel:}
\begin{itemize}
    \item Admins can log in through a secured backend dashboard.
    \item Perform CRUD operations (Create, Read, Update, Delete) on tour packages, including package descriptions, images, and pricing.
    \item Add, edit, or delete local tour guide information, linking them with relevant packages.
    \item Monitor booking activity, update availability, and ensure content accuracy in real-time.
\end{itemize}

The application ensures that both users and administrators interact through a clean, intuitive, and responsive interface powered by modern development frameworks. The design focuses on usability, accessibility, and seamless navigation.

\subsection{Summary}
In summary, the Odyssey Travel Agency Software is a feature-rich, scalable, and maintainable travel management system built to modernize the way travel bookings are conducted. It combines a dynamic frontend developed with HTML, CSS, Tailwind CSS, JavaScript, and Next.js with a powerful backend using Laravel and MySQL.

The system allows users to make informed decisions by browsing real-time travel offers, customizing their experience, and booking securely online. Meanwhile, the admin panel equips travel agency staff with efficient tools to manage packages and tour guide information. This dual functionality not only improves user satisfaction but also enhances the business capabilities of the agency.

The software adheres to core software engineering principles such as modularity, maintainability, security, and performance, making it a viable product for deployment in real-world travel agency operations.
