\section{Methodology}
This section outlines the systematic approach followed during the development of the travel agency website. The Software Development Life Cycle (SDLC) model was followed to ensure that the project was well-organized, efficient, and delivered successfully within the given timeframe.

\subsection{Planning}
The planning phase involved identifying project goals, features, and tools. The stack was finalized to include HTML, Tailwind CSS, JavaScript, and Next.js for the frontend, and Laravel with MySQL for the backend. Requirements were gathered for both the user and admin roles, and the expected user journey was mapped out—from viewing packages to payment completion.

\subsection{Design}
The design phase included both frontend and backend architectural planning. Wireframes were drawn to visualize page layouts such as Home, Package Listing, and Booking pages. The backend was structured using Laravel's MVC architecture. ER diagrams were created to model database relationships for users, packages, bookings, and tour guides.

\subsection{Implementation}
Frontend pages were built using Next.js for server-side rendering and faster load times. Tailwind CSS was used for consistent, responsive styling. On the backend, Laravel handled routing, controllers, models, and database migrations. Admin features like CRUD operations for tour packages and guide management were also implemented here.

\subsection{Testing}
Unit and integration testing were carried out to ensure all features worked as intended. Laravel’s built-in testing tools were used to test backend logic. Frontend behavior was manually tested across different browsers and devices. Form validation and session handling were thoroughly checked.

\subsection{Deployment}
After successful testing, the application was prepared for deployment. The backend (Laravel) was hosted on a PHP-compatible server, and the Next.js frontend was deployed via Vercel or a Node-compatible server. Environment variables were configured for secure communication with the database and third-party services.

\subsection{Future Enhancements}
Possible future improvements include integrating a real-time chatbot for customer support, adding review and rating features for packages, incorporating real-time availability for flights and hotels via APIs, and building a mobile app version of the platform using React Native.
